A Survey Wearable Device Risk Perceptions

### 2015-01-05 wearables_survey.tex
redid all of related work now. looks much better. `

\subsection{Ubiquitous Sensing}
{\color{red} This is plagiarized from our CHI paper! REWRITE!!! } Wearable devices, along with many other devices, are moving towards automated capture and ubiquitous  access~\cite{abowd2000charting}. More than ever, people will interact with sensors while carrying out daily activities, from a myriad of sources and for a variety of reasons: ``lifelogging'' devices to record their daily lives~\cite{hoyle2014privacy,dickie2004augmenting}, memory augmentation devices~\cite{chen2010augmenting,devaul2003memory,kalnikaite2010now}, smart homes that optimize living conditions~\cite{chan2008review,chan2009smart,edwards2001home}, devices that create augmented reality environments~\cite{azuma1997survey,azuma2001recent}, and even devices integrated into clothing \cite{anliker2001weararm}. The ubiquitous capture and storage of information naturally raises concerns about the preservation of privacy~\cite{palen2003unpacking}. Privacy in the field of ubiquitous computing relies on principles including notice, choice, and consent~\cite{langheinrich2001privacy}.

>>>>

\subsection{Ubiquitous Sensing}
At an unprecedented rate, we are moving towards automated capture and ubiquitous access~\cite{abowd2000charting}, whether it be through smartphones, smarthomes, networked devices, or, more recently, wearables. Wearbles have new capabilities which allow capture of unique data about the user and his/her surroundings. As information capture becomes pervasive and subtle, people are naturally concerned about privacy and security concerns ~\cite{palen2003unpacking}. Privacy in ubiquitous systems can be achieved my adhering to principles such as notice, choice, and consent ~\cite{langheinrich2001privacy}.
